### 2023-03-21 manuscript.tex
Citation fixing in progress [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/9f1d51557301a61b06b5b4dd934b2b478512567f.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/9f1d51557301a61b06b5b4dd934b2b478512567f/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4479098000

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/130d4210c6612bf03e9bd5333bdd51e40cf4a852/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/130d4210c6612bf03e9bd5333bdd51e40cf4a852}{stain/2022-fdo-paper@130d421}
on March 21, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/9f1d51557301a61b06b5b4dd934b2b478512567f/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/9f1d51557301a61b06b5b4dd934b2b478512567f}{stain/2022-fdo-paper@9f1d515}
on March 21, 2023.
